Ultra-deep $K_s$-band Imaging of the \textit{Hubble} Frontier Fields

### 2015-02-23 Paper0/ms.tex
merge again with new figure
Updates from ShareLaTeX
Push from sharelatex

@@

The final image and inverse-variance mosaics are provided as an ESO Phase 3 data product \xxx\ URL, as well as attached as a digital product to this manuscript (\xxx\ I think ApJSS can and wants to do this).  The images are scaled to an AB magnitude zeropoint ZP=26.0.  In the sections below we describe the characteristics of the mosaics in more detail.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Depth figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\epsscale{1.18}
\plotone{image_cutouts.pdf} % Figures/exposure_map.pdf
\caption{Image cutouts of the Abell 2744 field.  The \textit{RGB} and monochrome panels come from the sources as indicated; the cutouts are all $10\arcsec$ on a side.
\label{fig:cutout}}  
\end{figure}

@@

The final image and inverse-variance mosaics are provided as an ESO Phase 3 data product \xxx\ URL, as well as attached as a digital product to this manuscript (\xxx\ I think ApJSS can and wants to do this).  The images are scaled to an AB magnitude zeropoint ZP=26.0, which gives pixel values of order unity for faint galaxies.  In the sections below we describe the characteristics of the mosaics in more detail.
